Answers to reviewers' comments and list of modifications done\\ on paper SORO226\\ \LARGE{\textbf{Grounding the interaction: anchoring situated discourse in everyday human-robot interaction}}

### 2011-07-17 cover_letter.tex
cover letter: improved section 3.1

The Open World Assumption has important consequences on the reasoning
abilities of the system, since it prevents the classical ``negation by 
failure" and leads to tighter modelling requirement to locally ``close the
world" (for instance, the {\tt Color} class is defined as the equivalent of
the union of the 10 or so color instances we consider).

>>>>

The Open World Assumption has important consequences on the reasoning
abilities of the system, since it prevents the classical ``negation by 
failure". Lack of negation by failure leads to tighter modelling requirement to locally ``close the
world" (for instance, the {\tt Color} class is defined as the equivalent of
the union of 10 color instances).
